Sequential mobility patterns in people's daily life

### 2016-05-01 sq_mobility/sq_mobility_twitter.tex
new edits

\documentclass[a4paper,11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{lastpage,fancyhdr,graphicx}
\graphicspath{ {/figure/} }

\begin{document}
%\title{Mining sequential mobility patterns from semantic Twitter user trajectories}
\title{Sequential mobility patterns in people's daily life}
\author{Junjun Yin and Chao Zhang}
\maketitle

\section*{Abstract}
Understanding human mobility patterns

@@

\section*{Methods and Materials}
\subsection*{Geo-located Twitter Data}
In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it.
To ensure the complete coverage over Great Britain, we have set the bounding box to British Isles (lower left coordinates in (latitude, longitude): (49.497, -14.854) and upper right coordinates: (61.186, 2.637)), which also includes the whole area of Ireland and a part of France.
We have implemented a data crawler and continuously collected 7-month data (1st June – 31st December, 2014) with over 101.8 million tweets and 60 GB in size.
During the data collection phase, the data crawler did not encounter any issue regarding whether it exceeds the data quota by the 1$\%$ policy mentioned in (Hawelka et al., 2014).
It means we have managed to download all the geo-located tweets for the given bounding box.
In particular, to showcase the overall spatial coverage of the collected geo-located tweets, a density map of the Twitter user locations in British Isles for July 2014 is shown in Figure 4, where the collected points alone visually reveal the geography of cities and countries, e.g. the clusters with high density of tweets (in color red) correspond to the skeleton of major cities.

@@

\begin{figure}[ht]
	\includegraphics[width=1.0\linewidth]{./figure/gyration_chicago}
	\caption{{\bf The density map of the Twitter user locations for July 2014}}
	\label{Fig_gyration}
\end{figure}

\begin{figure}[ht]
	\includegraphics[width=1.0\linewidth]{./figure/Chicago_Shape}
	\caption{{\bf The density map of the Twitter user locations for July 2014}}
	\label{Fig_shape}
\end{figure}

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{lastpage,fancyhdr,graphicx}
\graphicspath{ {/figure/} }
\usepackage{authblk}

\begin{document}
%\title{Mining sequential mobility patterns from semantic Twitter user trajectories}
\title{Sequential mobility patterns in people's daily life}
\author[1]{Junjun Yin}
\author[2]{Chao Zhang}
\author[1]{Shaowen Wang\thanks{shaowen@illinois.edu}}
\affil[1]{CyberGIS Center for Advanced Digtial and Spatial Studies}
\affil[2]{Department of Computer Science}
\affil[ ]{University of Illinois at Urbana-Champaign, IL, 61801, USA}

\renewcommand\Authands{ and }

\maketitle

\section*{\centering Abstract}
Understanding human mobility patterns

@@

\section*{Related Work}

\section*{Methods and Materials}

\subsection*{Geo-located Twitter Data}
In this study, the geo-located tweets were downloaded using the Twitter Streaming API, where we specified a geographical bounding box as an area-of-interest to retrieve all the geo-located tweets that fall within it.
To ensure the complete coverage over Great Britain, we have set the bounding box to British Isles (lower left coordinates in (latitude, longitude): (49.497, -14.854) and upper right coordinates: (61.186, 2.637)), which also includes the whole area of Ireland and a part of France.
We have implemented a data crawler and continuously collected 7-month data (1st June – 31st December, 2014) with over 101.8 million tweets and 60 GB in size.
During the data collection phase, the data crawler did not encounter any issue regarding whether it exceeds the data quota by the 1$\%$ policy mentioned in (Hawelka et al., 2014).
It means we have managed to download all the geo-located tweets for the given bounding box.
In particular, to showcase the overall spatial coverage of the collected geo-located tweets, a density map of the Twitter user locations in British Isles for July 2014 is shown in Figure 4, where the collected points alone visually reveal the geography of cities and countries, e.g. the clusters with high density of tweets (in color red) correspond to the skeleton of major cities.

@@

\begin{figure}[ht]
	\includegraphics[width=1.0\linewidth]{./figure/gyration_chicago}
	\caption{{\bf The distribution of the radius of gyrations for Twitter users in Chicago}}
	\label{Fig_gyration}
\end{figure}

\begin{figure}[ht]
	\includegraphics[width=1.0\linewidth]{./figure/Chicago_Shape}
	\caption{{\bf The shape of Twitter user mobility in Chicago for year 2014}}
	\label{Fig_shape}
\end{figure}

\begin{figure}[ht]
	\includegraphics[width=1.0\linewidth]{./figure/firsttime}
	\caption{{\bf The shape of Twitter user mobility in Chicago for year 2014}}
	\label{Fig_shape}
\end{figure}

\section*{Results}

\section*{Discussion and Conclusion}
